Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-07-01 snapshot_system/result.tex
Updated terminology in plots.
cleaned up the paper directory (moved all pdf figures to the images dir) and corrected references.
added srb comparison text, updated references throughout paper.

\subsection{System Performance}
{\bf Single VM Backup} We start the evauluation of our system by examine the normal warmed-up
backup scenario - taking a snapshot of a VM which already has old backups exist. To simulate this
scenario, we pick one 40GB VM from the data set, make an initial snapshot backup, then
evaulate the system performance on the second snapshot backup. We repeat such procedure
under different CDS memory usage settings, the results of backup time break down are shown in
firure~\ref{fig:single_vm_backup}.

@@

\subsection{Comparison with Other Approaches}
\subsubsection{Extreme Binning}
%\comments{
    %this version of the figure is vertical
    \begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Extreme-Binning Efficiency},
            ybar,
            bar width=1.00cm,
            symbolic x coords={SRB,VC},
            xlabel={Algorithm},
            ylabel={Dedup. Efficiency (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            xtick=data, %without this the symbolic coords may be repeated as filler
            enlarge x limits=0.6, %used to push plots towards center
            ymin=85,
            %ymax=100,
            nodes near coords,
            nodes near coords align={vertical},
            ]
            \addplot coordinates {(SRB,89.99) (VC,90.51)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
  \label{fig-exbin-efficiency}
\end{figure}
%}
%same figure as above but horizontal (better for only two data points)
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Extreme-Binning Efficiency},
            xbar,
            width=7cm,
            height=3.5cm,
            %bar width=0.75cm,
            symbolic y coords={SRB,VC},
            xlabel={Dedup. Efficiency (\%)},
            %ylabel={Algorithm},
            %extra x ticks={4.5,5.5,6.5} %to add extra ticks
            ytick=data, %without this the symbolic coords may be repeated as filler
            enlarge y limits=0.5,
            xmin=85,
            xmax=92, %otherwise label overlaps with right border
            nodes near coords,
            nodes near coords align={horizontal},
            ]
            \addplot coordinates {(89.99,SRB) (90.51,VC)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
  \label{fig-exbin-efficiency}
\end{figure}

\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Ex-Binning Efficiency},
            xlabel={Number of VMs added},
            ylabel={Dedup. Efficiency (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot[color=blue,mark=none] table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison.txt};
            \addplot[densely dotted, color=red,mark=none] table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
            \addplot[loosely dotted, color=brown,mark=none] table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
            \addplot[densely dashed,color=black,mark=none] table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
            \legend{SRB,VC (1\%CDS),VC (2\%CDS),VC (4\%CDS)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
    Stateless Routing with Binning and VC.}
  \label{fig-exbin-efficiency-graph}
\end{figure}

>>>>

\subsection{System Performance}
{\bf Single VM Backup} We start the evauluation of our system by examine the normal warmed-up
backup scenario - taking a snapshot of a VM which already has old backups exist. To simulate this
scenario, we pick one 40GB VM from the data set, make an initial snapshot backup, then
evaulate the system performance on the second snapshot backup. We repeat such procedure
under different CDS memory usage settings, the results of backup time break down are shown in
Figure~\ref{fig:single_vm_backup}.

\begin{figure}
    \centering
    \includegraphics[width=3in]{figures/single_backup_time.pdf}
    \caption{Backup times for varying CDS sizes}
    \label{fig:single_vm_backup}
\end{figure}

@@

\subsection{Comparison with Other Approaches}
\subsubsection{Stateless Routing with Binning}
We compare our system with Stateless Routing with Binning (SRB) in terms of
both backup time and deduplication efficiency. SRB is the same as the stateless
routing algorithm given in the Extreme Binning\cite{??} paper. the
deduplication efficiency is compared in
Figure~\ref{fig-exbin-efficiency-graph}, showing the deduplication efficiency
(percent of duplicate chunks which are deduped) of SRB and VC with several
different CDS sizes. From the graph you can see that VC provides similar or
better deduplication efficiency in all cases. In Figure~\ref{fig:srb_vs_vc} you
can see simulated backup times using actual throughput numbers from our test
backup cluster, and VC outperforms SRB mainly due to significantly fewer index
lookups (since SRB uses hash-partitioning, all lookups are essentially random
and caching will be largely innefective).  \emph{Should we use one of the two
bar charts, or the graph? I am thinking the graph, but I'll leave the two bar
charts in the paper until we decide? If we use the bar charts some tex will
have to be changed. We could also add each of the CDS sizes to the bar chart
and have 4 bars instead of 2.}
%\comments{
    %this version of the figure is vertical
    \begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Extreme-Binning Efficiency},
            ybar,
            bar width=1.00cm,
            symbolic x coords={SRB,VC},
            xlabel={Algorithm},
            ylabel={Dedup. Efficiency (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            xtick=data, %without this the symbolic coords may be repeated as filler
            enlarge x limits=0.6, %used to push plots towards center
            ymin=85,
            %ymax=100,
            nodes near coords,
            nodes near coords align={vertical},
            ]
            \addplot coordinates {(SRB,89.99) (VC,90.51)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
  \label{fig-exbin-efficiency1}
\end{figure}
%}
%same figure as above but horizontal (better for only two data points)
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Extreme-Binning Efficiency},
            xbar,
            width=7cm,
            height=3.5cm,
            %bar width=0.75cm,
            symbolic y coords={SRB,VC},
            xlabel={Dedup. Efficiency (\%)},
            %ylabel={Algorithm},
            %extra x ticks={4.5,5.5,6.5} %to add extra ticks
            ytick=data, %without this the symbolic coords may be repeated as filler
            enlarge y limits=0.5,
            xmin=85,
            xmax=92, %otherwise label overlaps with right border
            nodes near coords,
            nodes near coords align={horizontal},
            ]
            \addplot coordinates {(89.99,SRB) (90.51,VC)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
  \label{fig-exbin-efficiency2}
\end{figure}

%graph comparing extreme binning (SRB) with CDS model (VC) for different cds percentages
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Ex-Binning Efficiency},
            xlabel={Number of VMs added},
            ylabel={Dedup. Efficiency (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot[color=blue,mark=none] table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison.txt};
            \addplot[densely dotted, color=red,mark=none] table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
            \addplot[loosely dotted, color=brown,mark=none] table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
            \addplot[densely dashed,color=black,mark=none] table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
            \legend{SRB,VC (1\%CDS),VC (2\%CDS),VC (4\%CDS)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
    Stateless Routing with Binning and VC.}
  \label{fig-exbin-efficiency-graph}
\end{figure}

### 2013-07-01 snapshot_system/snapshot.tex
update grpah
Updated terminology in plots.
cleaned up the paper directory (moved all pdf figures to the images dir) and corrected references.
added srb comparison text, updated references throughout paper.

\item \textbf{VM-centric file system block management.}
When a chunk is not detected as a duplicate to any existing chunk, this chunk will be written
to the file system. Since the backend file system typically uses a large block size such as 64MB, each VM will 
accumulate small local chunks. We manage this accumulation process using an append-store  scheme
and discuss this in details in Section~\ref{sect:arch}.
The system allows all machines conduct the backup in parallel in different machines, and each machine
conducts the backup of one VM at a time, and thus only requires a write  buffer for one VM.

CDS chunks are stored in a separate
append-store instance. In this way, each file block for non-CDS chunks is associated with one VM
and does not contain any CDS chunk. 
\end{itemize}

@@

\begin{figure}
\centering
%\epsfig{file=log-log.disk.pdf,width=3in}
%source ../vm_snapshot_sim/images/log-log.disk.eps
 \includegraphics[width=3in]{log-log-disk.pdf}
\caption{Duplicate frequency versus  chunk ranking in a log scale.}
\label{fig:Datazipf}
\end{figure}

@@

\begin{table}
    \begin{tabular}{llll}
    Data size (GB) & 1\%    & 2\%    & 4\%    \\
    14.6           & 18.6\% & 22.1\% & 31.4\% \\
    28.1           & 19.5\% & 26.2\% & 38.8\% \\
    44.2           & 21.7\% & 26.5\% & 36\%   \\
    61.6           & 23.2\% & 32.9\% & 35\%   \\
    74.2           & 23.6\% & 33.6\% & 37.5\% \\
    \end{tabular}
    \caption{Deduplication effectiveness of top k\% of global index}
    \label{tab:cds}
\end{table}

\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={CDS Coverage},
            xlabel={Total number of chunks stored},
            ylabel={CDS Coverage (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            %legend pos=outer north east,
            legend columns=2,
            legend style={
                at={(0.5,-0.2)},
            anchor=north}
            ]
            \addplot[color=blue,mark=*] table[x=InputChunks,y=A1] {figures/cds_coverage.txt};
            \addplot[color=blue,mark=square*] table[x=InputChunks,y=A2] {figures/cds_coverage.txt};
            \addplot[color=blue,mark=triangle*,mark size=3] table[x=InputChunks,y=A4] {figures/cds_coverage.txt};
            \addplot[densely dashed,color=red,mark=*] table[x=InputChunks,y=T1] {figures/cds_coverage.txt};
            \addplot[densely dashed,color=red,mark=square*] table[x=InputChunks,y=T2] {figures/cds_coverage.txt};
            \addplot[densely dashed,color=red,mark=triangle*] table[x=InputChunks,y=T4] {figures/cds_coverage.txt};
            \legend{Measured (1\%CDS),Measured (2\%CDS),Measured (4\%CDS),Predicted (1\%CDS),Predicted (2\%CDS),Predicted (4\%CDS)};
            \end{axis}
    \end{tikzpicture}
  \caption{fixed-alpha predicted vs. actual CDS coverage as data size increases.}
  \label{fig-vo-links}
\end{figure}

>>>>

\item \textbf{VM-centric file system block management.}
When a chunk is not detected as a duplicate to any existing chunk, this chunk will be written
to the file system. Since the backend file system typically uses a large block size such as 64MB, each VM will 
accumulate small local chunks. We manage this accumulation process using an append-store  scheme
and discuss this in details in Section~\ref{sec:arch}.
The system allows all machines conduct the backup in parallel in different machines, and each machine
conducts the backup of one VM at a time, and thus only requires a write  buffer for one VM.

CDS chunks are stored in a separate append-store instance. In this way, each
file block for non-CDS chunks is associated with one VM and does not contain
any CDS chunks. 
\end{itemize}

@@

\begin{figure}
\centering
%\epsfig{file=log-log.disk.pdf,width=3in}
%source ../vm_snapshot_sim/images/log-log.disk.eps
 \includegraphics[width=3in]{figures/log-log-disk.pdf}
\caption{Duplicate frequency versus  chunk ranking in a log scale.}
\label{fig:Datazipf}
\end{figure}

@@

\comments{ %this table is superceded by the graph below it
\begin{table}
    \begin{tabular}{llll}
    Data size (GB) & 1\%    & 2\%    & 4\%    \\
    14.6           & 18.6\% & 22.1\% & 31.4\% \\
    28.1           & 19.5\% & 26.2\% & 38.8\% \\
    44.2           & 21.7\% & 26.5\% & 36\%   \\
    61.6           & 23.2\% & 32.9\% & 35\%   \\
    74.2           & 23.6\% & 33.6\% & 37.5\% \\
    \end{tabular}
    \caption{Deduplication effectiveness of top k\% of global index}
    \label{tab:cds}
\end{table}
}

\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={CDS Coverage},
            xlabel={Total number of chunks stored},
            ylabel={CDS Coverage (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            %legend pos=outer north east,
            legend columns=2,
            legend style={
                at={(0.5,-0.2)},
            anchor=north}
            ]
            \addplot[color=blue,mark=*] table[x=InputChunks,y=A1] {figures/cds_coverage.txt};
            \addplot[color=blue,mark=square*] table[x=InputChunks,y=A2] {figures/cds_coverage.txt};
            \addplot[color=blue,mark=triangle*,mark size=3] table[x=InputChunks,y=A4] {figures/cds_coverage.txt};
            \addplot[densely dashed,color=red,mark=*] table[x=InputChunks,y=T1] {figures/cds_coverage.txt};
            \addplot[densely dashed,color=red,mark=square*] table[x=InputChunks,y=T2] {figures/cds_coverage.txt};
            \addplot[densely dashed,color=red,mark=triangle*] table[x=InputChunks,y=T4] {figures/cds_coverage.txt};
            \legend{Measured (1\%CDS),Measured (2\%CDS),Measured (4\%CDS),Predicted (1\%CDS),Predicted (2\%CDS),Predicted (4\%CDS)};
            \end{axis}
    \end{tikzpicture}
  \caption{fixed-alpha predicted vs. actual CDS coverage as data size increases.}
  \label{fig-cds-coverage}
\end{figure}
